FTLR proof cases

### 2018-03-09 fully-abstract-comp/ftlr-proof-cases.tex
Add a lemma to be proven.
Fix readXCond to require that ms is safe.

@@

\begin{lemma}
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $\npair{(b,e)}\in\readCond{l,W}$
  \item $a \in [b,e]$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \end{itemize}
  Then $\npair[n']{(\ms_S(a),\ms_T(a))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
  Additionally, if
  \begin{itemize}
  \item $\npair{(b,e)}\in\writeCond{l,W}$
  \end{itemize}
  Then $\memSat{(\ms_S[a\mapsto 0],\stk,\ms_\stk,\ms_T[a\mapsto 0])}{W_M'}$.
\end{lemma}
\begin{proof}
  From $\npair{(b,e)}\in\readCond{l,W}$, we get an $r \in \addressable{\lin,
    \pwheap}$ and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that $\pwheap(r)
  \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$.

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \readCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$ and $\npair{(\baddr,\eaddr)}\in \readCond{\lin,W}$.
From Lemma~\ref{lem:readcond-writecond-work}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

>>>>

\begin{lemma}[readXCondition implies readCondition]
  \label{lem:readXCond-readCond}
  If $\npair{(b,e)}\in\xReadCond{\lin,W}$, then $\npair{(b,e)}\in\readCond{\lin,W}$.
  \dominique{TODO}
\end{lemma}

@@

\begin{lemma}[readCondition works]
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $\npair{(b,e)}\in\readCond{l,W}$
  \item $a \in [b,e]$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \end{itemize}
  Then $\npair[n']{(\ms_S(a),\ms_T(a))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
  Additionally, if
  \begin{itemize}
  \item $\npair{(b,e)}\in\writeCond{l,W}$
  \end{itemize}
  Then $\memSat{(\ms_S[a\mapsto 0],\stk,\ms_\stk,\ms_T[a\mapsto 0])}{W_M'}$.
\end{lemma}
\begin{proof}
  From $\npair{(b,e)}\in\readCond{l,W}$, we get an $r \in \addressable{\lin,
    \pwheap}$ and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that $\pwheap(r)
  \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$.

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

@@

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$ and $\npair{(\baddr,\eaddr)}\in \xReadCond{\lin,W}$.
From Lemmas~\ref{lem:readcond-writecond-work} and~\ref{lem:readXCond-readCond}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
